Differential Expression - HBCC - DLPFC - Dx

### 2020-08-24 individual-cohorts/split_by_analysis/HBCC_DLPFC_DE_Diagnosis.Rmd
remove samples based on age threshold
update provenance

# Github link
thisRepo <- getRepo(repository = "CommonMindConsortium/covarr-de", ref="branch", refName='master')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('individual-cohorts/split_by_analysis/',thisFileName))
```

@@

@@

# Get gene lengths
counts = 'syn21886235'
ALL_USED_IDs = counts
counts = downloadFile(counts) %>% data.frame()
gene_lengths = counts[,c("Geneid", "Length")] %>% 
  dplyr::rename(gene_id = Geneid)
rm(counts)

@@

multiplot(plotlist = pl, cols = 3)
```

>>>>

# Github link
thisRepo <- getRepo(repository = "CommonMindConsortium/covarr-de", ref="branch", refName='modify-cqn-implementation')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('individual-cohorts/split_by_analysis/',thisFileName))
```

@@

# Remove ages under 17
COVARIATES <- COVARIATES[COVARIATES$ageOfDeath >= 17,]
NEW.COUNTS <- NEW.COUNTS[names(NEW.COUNTS) %in% rownames(COVARIATES)]
CQN.GENE_EXPRESSION <- CQN.GENE_EXPRESSION[names(CQN.GENE_EXPRESSION) %in% rownames(COVARIATES)]

@@

# Get gene lengths
counts = 'syn21886235'
ALL_USED_IDs = c(ALL_USED_IDs, counts)
counts = downloadFile(counts) %>% data.frame()
gene_lengths = counts[,c("Geneid", "Length")] %>% 
  dplyr::rename(gene_id = Geneid)
rm(counts)

@@

multiplot(plotlist = pl, cols = 3)
```
### Source Code
[markdown file](`r thisFile`)
